Hydras \& Co.

### 2023-10-13 doc/chap-intro-goedel.tex
Small wording fixes and improvements in Goedel intro chapter.

It was the first computer verified proof 
the essential incompleteness of arithmetic.
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

@@

 \begin{itemize}
 \item Historical interest on G\"{o}del's proof and its mechanizations, as shown by the numerous litterature on this topic
   (for instance \cite{smullyan1992godel, Hofstadter1999Godel, GoedelCassou}).

@@

        For technical reasons --- mainly in order to make simpler the installation and use of its sub-libraries, we split the project
into two main parts: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

Some changes are made to the aforementionned libraries, mainly because of the recent evolution of coq and its libraries. Nevertheless, the definitions, lemmas and theorems of the original contribution have been kept in this new release.

>>>>

It was the first computer verified proof of
the essential incompleteness\footnote{Todo: explain ``essential''} of Peano arithmetic.
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

@@

\begin{todo}
  Cite~\cite{Dowek2023}.
\end{todo}

 \begin{itemize}
 \item Historical interest in G\"{o}del's proof and its mechanizations, as shown by the abundant litterature on this topic
   (for instance \cite{smullyan1992godel, Hofstadter1999Godel, GoedelCassou}).

@@

        For technical reasons --- mainly in order to simplify the installation and use of its sub-libraries, we split the project
into two main parts: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

Some changes are made to the aforementionned libraries, mainly because of the recent evolution of Coq and its libraries. Nevertheless, the definitions, lemmas and theorems of the original contribution have been preserved in this new release.
